%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CV template for ProDigital proposal
%
% Author: Martin Hoelzer
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS - JUST LEAVE THIS AT IS IS
%----------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article} % Default font size and paper size
\usepackage{fontspec} % For loading fonts
\usepackage{eurosym}

%% IF YOU WANT TO COMPILE THIS TEX LOCALLY, COMMENT THE FOLLOWING LINES IF THE FONTS ARE NOT INSTALLED
\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Fontin-Regular.otf}[
BoldFont       = Fontin-Bold.otf ,
ItalicFont     = Fontin-Italic.otf ,
SmallCapsFont  = Fontin-SmallCaps.otf ]
%% UNTIL HERE 

\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages
\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors
\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}
\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document
\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections


%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	MAIN DOCUMENT - PLEASE ENTER YOUR DATA HERE
%
%	Some basic LaTeX commands: 
%
%	A '%' marks a comment that will not be shown in the final PDF
%	If you want to remove content, just comment the line(s) with a leading '%'
%
%	When you open an environment with a '{' you need to close it with a corresponding '}'!
%
%	\textbf{TEXT} 						makes TEXT bold font
%	\emph{TEXT} 						makes TEXT italics font
%	\textsc{TEXT}						makes TEXT small caps font
%	\small \footnotesize \Huge ...		defines font sizes
%	\begin{tabular} ... \end{tabular} 	defines a table environment
%										inside a table environment a '&' sign splits between columns 
%										inside a table a '\\' marks the end of a row
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} % Removes page numbering
\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\section{ALI AMROLLAHI}
\begin{tabular}{rl}
\vspace{0.2cm}
\textbf{Email:}   &  \href{mailto:aliamrollahiii2002@gmail.com}{Aliamrollahiii2002@gmail.com}\\
\vspace{0.2cm}
\textbf{Github:} 					& \href{https://github.com/Aliamrol}{github.com/Aliamrol} \\  
\vspace{0.2cm}
\textbf{linkedin:} 					& \href{https://www.linkedin.com/in/ali-amrollahi-12383022a/}
{linkedin.com/Aliamrol} \\  
\vspace{0.2cm}
\textbf{Phone:} 					& 
+989057510010 \\

\end{tabular}
\\
%----------------------------------------------------------------------------------------
%	SCIENTIFIC EDUCATION
%----------------------------------------------------------------------------------------
\vspace{0.5cm}
\section{Education}
%%BEGIN TABLEث
\begin{tabular}{r|l}	

\multicolumn{2}{c}{} \\	% this is just an empty row

08/2021 - 08/2025\\(expected) 							& \textsc{Bachelor of Science, Computer Engineering}\\
          							& Amirkabir University of Technology  \\
\\

\end{tabular}
%%END TABLE
\\

\vspace{0.5cm}

\section{Work Experience}
\vspace{0.2cm}

\begin{itemize}
    \item \textbf{Android Developer Freelance } (Sep 2023 - sep 2024) \newline
    Developed and released an Android application for a consulting company to assist farmers with their schedules. The application was developed using Bloc, and Cubit architectures in Flutter. 
    \vspace{0.5cm}
    \item \textbf{Android Developer Intern in Langeek} (june 2023 - aug 2023)\newline Learned about Bloc, Cubit, Dio, Freezed, Locator, Clean Architecture, and developed a review card.
\end{itemize}

\vspace{0.5cm}

\section{Technical skills} 

\begin{itemize}
    \item \textbf{Languages: }Kotlin, Java, Dart, Python
    \vspace{0.2cm}
    \item \textbf{Android Development:} 
        \begin{itemize}
            \vspace{0.1cm}
            \item Proficient in Jetpack Compose and Flutter
            \vspace{0.1cm}
            \item Knowledgeable in Clean Architecture, MVP, MVVM and Bloc architectural patterns
            \item Understanding of SOLID principles and Dependency Injection
            \vspace{0.1cm}
            \item Experience with Retrofit, Coroutines and RESTful API 
            \vspace{0.1cm}
        \end{itemize}
        \vspace{0.2cm}
    \item \textbf{Database} : MySQL, RoomDB
    \vspace{0.2cm}
    \item \textbf{Tools: }Android Studio , Git , Linux
    \vspace{0.2cm}
    \item \textbf{Methodologies: }Agile, Scrum
\end{itemize}
\vspace{0.5cm}




\section{Notable Projects}  

\begin{small}
\textbf{DigiKalaDemo}\\
A demo Android application inspired by the famous Digikala e-commerce app. Built using modern Android development practices and technologies such as MVVM architecture, SOLID principles, Coroutines, Kotlin Flow, RoomDB, Hilt for Dependency Injection, and DataStore for local data persistence. This project demonstrates clean architecture, modular code design, and seamless user experience with Jetpack Compose.
[\href{https://github.com/aliamrol/digikalademo}{Link}]


\textbf{Baghmoshaver}\\
developed and released an Android application for a consulting company to assist farmers with their schedules. The application was developed using Bloc, and Cubit architectures in Flutter. [\href{https://cafebazaar.ir/app/com.example.bagh_moshaver}{Link}]
\end{small}

\textbf{Discord}\\
This is a demo version of a real Discord application using Java and JavaFX where you can create an account, log into
your account, have private chats with your friends, and stay connected. Additionally, you can
create servers, create channels and groups within the servers, and chat with a group of friends. It also
includes features like blocking users, adding them to your friends list, and more.
[\href{https://github.com/Aliamrol/Discord}{Link}]

\textbf{ComposeDelicious}\\
A Jetpack Compose-based Android app to display a list of foods with their details, nutritional information, and related recipes. This project is a part of my learning journey with Jetpack Compose, focusing on modern Android UI development.
[\href{https://github.com/Aliamrol/ComposeDelicious}{Link}]


\end{document}